\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-12-06 Final Paper/PaperJLin.tex
Started Adding liberalism tables

\usepackage{fullpage} %full page typesetting
\usepackage{setspace} %allows for non-singlespacing
\usepackage{graphicx} %graphics capabilities
\usepackage{latexsym} %extra symbols
\usepackage{rotating} %rotation for figures
\usepackage{longtable} %tables that fill more than a single page
%\usepackage{hyperref} %hypertext links in the document
\usepackage{natbib} %better bibliographies
\usepackage{authblk} %author and affiliation in opening
\usepackage{mathpazo} %use palatino font, rather than times
\usepackage{appendix}
\usepackage{lscape}
\usepackage{tabulary}
\usepackage[nottoc]{tocbibind}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=cyan]{hyperref}
\usepackage{ifthen}
\usepackage{float}
\usepackage{subcaption}
\usepackage{mwe}

@@

@@

@@

@@

@@

@@

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Middle East}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
			\hline
			Small Town&.5796 & .4447 \\
			&(.3041)  & (.6314)\\
			Suburban&.5968 &.3318 \\
			& (.3478)  & (.6740)\\
			Urban &- & .4440\\
			&- & (.5626)\\
			Constant& 61311*** &1.953 \\
			& (.9217)  & (.1.813)\\
			N&439 & 251\\
			$R^2$&0.2978 & 0.1484 \\
			\hline 
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table10}
	\end{table}
\end{singlespace}

@@

@@

@@

@@

@@

\section{Average Self-Placement Ideology by Country}
\label{AppendixF}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Ideology/Germany}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{Ideology/France}
	\end{subfigure}
	\caption[ Western Europe]
	{\tb{ Average Self-Placement Ideology by Place of Residence for Western Europe} }
	\label{fig:mean and std of nets}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Ideology/Austria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{Ideology/Czech}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{Ideology/Poland}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{Ideology/Slovakia}
	\end{subfigure}
	\caption[ Central Europe ]
	{\tb {Average Self Placement Ideology by Place of Residence for Central Europe} }
	\label{figureF3}
\end{figure}

>>>>

\usepackage{fullpage} %full page typesetting
\usepackage{setspace} %allows for non-singlespacing
\usepackage{graphicx} %graphics capabilities
\usepackage{latexsym} %extra symbols
\usepackage{rotating} %rotation for figures
\usepackage{longtable} %tables that fill more than a single page
%\usepackage{hyperref} %hypertext links in the document
\usepackage{natbib} %better bibliographies
\usepackage{authblk} %author and affiliation in opening
\usepackage{mathpazo} %use palatino font, rather than times
\usepackage{appendix}
\usepackage{lscape}
\usepackage{tabulary}
\usepackage[nottoc]{tocbibind}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=cyan]{hyperref}
\usepackage{ifthen}
\usepackage{float}
\usepackage{subcaption}
\usepackage{mwe}
\usepackage{caption}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Mexico}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Peru}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Central/Latin America} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Central/Latin America} }
	\label{America}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Germany}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/France}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Western Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Western Europa} }
	\label{WestEuro}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Austria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
	\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Czech}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Poland}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Slovakia}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Central Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Central Europe} }
	\label{CentEuro}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Finland}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Iceland}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Sweden}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Scandinavia} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Scandinavia} }
	\label{Scandinavia}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Bulgaria}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Greece}
	\end{subfigure}
	\vskip\baselineskip
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Montenegro}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Romania}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Southwestern Europe} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Southwestern Europe} }
	\label{SWEuro}
\end{figure}

@@

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{IdeologyCoef/Latvia}}
	\caption[ \tb{Self-Placement Ideology - Eastern Europe} ]
{\tb {Coefficient Plots for Self-Placement Ideology in Eastern Europe} }
\label{EastEuro}
\end{figure}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Middle East}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
			\hline
			Small Town&.5796 & .4447 \\
			&(.3041)  & (.6314)\\
			Suburban&.5968 &.3318 \\
			& (.3478)  & (.6740)\\
			Urban &- & .4440\\
			&- & (.5626)\\
			Constant& 6.1311*** &1.953 \\
			& (.9217)  & (1.813)\\
			N&439 & 251\\
			$R^2$&0.2978 & 0.1484 \\
			\hline 
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table10}
	\end{table}
\end{singlespace}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Israel}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Turkey}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Middle East} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Middle East} }
	\label{MidEast}
\end{figure}

@@

\begin{figure}[H]    \centering
	{	 \includegraphics[width=.5\textwidth]{IdeologyCoef/SouthAfrica}}
	\caption[ \tb{Self-Placement Ideology - Africa} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Africa} }
	\label{Africa}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/Japan}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/SouthKorea}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Asia} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Asia} }
	\label{Asia}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{IdeologyCoef/NewZealand}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}  
		\centering 
		\includegraphics[width=\textwidth]{IdeologyCoef/Philippines}
	\end{subfigure}
	\caption[ \tb{Self-Placement Ideology - Pacific Islands} ]
	{\tb {Coefficient Plots for Self-Placement Ideology in Pacific Island} }
	\label{Pacific}
\end{figure}

@@

Now, we proceed to break down this general analysis by the same regions used to test the \e{Sekf-Identified Ideology} Hypothesis.

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Central/Latin America}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Mexico (2012)}&\tb{Mexico (2015)} &\tb{Peru}\\
			\hline
			Small Town&-.2407 & .3685*& - \\
			&(.4166)  & (.2180)&-\\
			Suburban&- &- &-\\
			& -  & -&-\\
			Urban &-.0589 & .1503&-.014\\
			&(.3661) & (.1577)&(.1250)\\
			Constant& 2.8517*** &3.6772***&2.760*** \\
			& (..6696)  & (.4178&(.3451)\\
			N&110 & 335&262\\
			$R^2$&0.0575 & 0.0321&0.0589 \\
			\hline 
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{CentAmerLib}
	\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Western Europe}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{Germany}&\tb{France} \\
			\hline
			Small Town& .0236 & -.0362   \\
			&(.1004)  & (.0648)\\
			Suburban&-.1950&-.1163 \\
			&(.1549) &  (.0926) \\
			Urban & .1514&.0188 \\
			&(.1195) &(.0846) \\
			Constant&2.920*** &2.001*** \\
			&(.3134) &(.2402) \\
			N&418& 1,159\\
			$R^2$&0.0873 & 0.0512 \\
			\hline 
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{WELib}
\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Central Europe}}
		\begin{tabulary}{\linewidth}{l c c c }
			\\
			\hline
			\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} \\
			\hline
			Small Town &.0045 &.1837  &-.0045   \\
			&(.1289)&(.1167) &(.0778)  \\
			Suburban& .0362 &.3035  &-.2401**   \\
			&(.1345) &(.1967) &(.1164)\\
			Urban&-.1473&.4128***  &-.0112    \\
			&(.1622)& (.1166)  &(.1008)    \\
			Constant&4.3364*** &3.3739***  &2.637***     \\
			N&246 & 448  & 711   \\
			$R^2$&0.0674&0.1258  &0.0546  \\
			\hline 
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{CELib}
\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Issue Stances - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			Small Town& -.0501 &.1522 & -.1209 \\
			&(.1997) & (.1830) & (.1828) \\
			Suburban&-.0150&.2700  &-.1410  \\
			&(.1651) &(.1852) & (.1745) \\
			Urban &.0677 &.1158  & -.0144 \\
			&(.2131) & (.1819) & (.1578) \\
			Constant&3.9752*** &3.995***  & 3.6204*** \\
			&(.5452) &(.3722) & (.4453) \\
			N&198&372 &284  \\
			$R^2$&0.1154&.1055  & 0.0362 \\  
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{ScanLib}
\end{table}
\end{singlespace}

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Southwestern Europe}}
		\begin{tabulary}{\linewidth}{l c c c c c c}
			\\
			\hline
			\tb{Residence}& \tb{Bulgaria}& \tb{Greece ('12)}& \tb{Greece ('15)} & \tb{Montenegro} & \tb{Romania ('12)} & \tb {Romania ('14)}\\
			\hline
			Small Town& -.0295&-.3396 & & & &  \\
			&(.1228) &(.2166)  &  &  &  &   \\
			Suburban& .3420***&-.4875** &  &  &  &  \\
			&(.1111)& (.2118)  &  &  &  & \\
			Urban&.2230& -.4093** &  &  &  &  \\
			&(.1663)& (.1729) &   &   &  &   \\
			Constant&3.0603***&2.360***  &  &  &  &  \\
			&(.3741)& (.5231)  &  &  &  &  \\
			N&391 & 329  &   &  &   &  \\
			$R^2$&0.0899& 0.1420  &  &  &  &  \\
			\hline
\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{SWELib}
\end{table}
\end{landscape}

@@

%\section{Average Self-Placement Ideology by Country}
%\label{AppendixF}

%\begin{figure}[H]
%	\centering
%	\begin{subfigure}[b]{0.475\textwidth}
%		\centering
%	\includegraphics[width=\textwidth]{Ideology/Germany}
%	\end{subfigure}
%	\hfill
%	\begin{subfigure}[b]{0.475\textwidth}  
%		\centering 
%		\includegraphics[width=\textwidth]{Ideology/France}
%	\end{subfigure}
%	\caption[ Western Europe]
%	{\tb{ Average Self-Placement Ideology by Place of Residence for Western Europe} }
%	\label{fig:mean and std of nets}
%\end{figure}

%\begin{figure}[H]
%	\centering
%	\begin{subfigure}[b]{0.475\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{Ideology/Austria}
%	\end{subfigure}
%	\hfill
%	\begin{subfigure}[b]{0.475\textwidth}  
%	\centering 
%		\includegraphics[width=\textwidth]{Ideology/Czech}
%	\end{subfigure}
%	\vskip\baselineskip
%	\begin{subfigure}[b]{0.475\textwidth}   
%		\centering 
%		\includegraphics[width=\textwidth]{Ideology/Poland}
%	\end{subfigure}
%	\quad
%	\begin{subfigure}[b]{0.475\textwidth}   
%		\centering 
%		\includegraphics[width=\textwidth]{Ideology/Slovakia}
%	\end{subfigure}
%	\caption[ Central Europe ]
%	{\tb {Average Self Placement Ideology by Place of Residence for Central Europe} }
%	\label{figureF3}
%\end{figure}

%\clearpage
